---
title: "Data_Structures_01152019"
author: "Nina Dyatchenko"
date: "February 13, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#  Likelihood 2/5/2019 in class
Likelihood of 7 successes out of 11 trials. Binomial experiment:
```{r}
Lbin_11_7 <-  function(p){
  p^7 * (1-p)^4
}
curve(Lbin_11_7, from = 0, to = 1)

Lbin_11_7 <- function(p){
  p^7 * (1-p)^4
}
```
#  Homework 3

Squared slope (derivative) for 7 successess out of 11 trials:
```{r}
DerivL_11_7 <- function(p){
  ((7-11*p)/(p*(1-p)))^2
}

mean(DerivL_11_7(seq(from = 0.001, to = 0.999, by = 0.001)))
```
The mean squared slope is 106123.5

Likelihood of 70 successes out of 110 trials. Binomial experiment:
```{r}
DerivL_110_70 <- function(p){
  ((70-110*p)/(p*(1-p)))^2
}
mean(DerivL_110_70(seq(from = 0.001, to = 0.999, by = 0.001)))
```

The mean squared slope for 70 successes out of 110 trials is 10612354. Which is
100 times larger than average slope of 7 successes out of 11 trials.

Conclusion: larger sample size n contributes to a stipper slope. 
