---
title: "Data_Structures_01152019"
author: "Nina Dyatchenko"
date: "February 19, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Clinical Trial Story

### Negative Binomial
pnbinom(q, size, prob, lower.tail = TRUE, log.p = FALSE)

```{r}
1-pbinom(q = 149, size = 10000, prob = 0.95, log = FALSE)

Binom <- function(n, k, p){
  choose(n, k) * (p^k)  * (1-p)^(n-k)
}
Binom(10000, 150, 0.05)
```
We are almost sure that we find 150 patients from 10,000 sample.

The probability is 9.6e-83 that we need to review more than 10,000 records 
to identify 150 patients, having the probability of the event p = 0.05.


### Geometric distribution
pgeom(q, prob, lower.tail = TRUE, log.p = FALSE) - probability
prob -a numeric vector in the range [0, 1] that specifies the probability of 
a success in a Bernoulli trial.
q - a numeric vector in the range [0, Inf) that specify the quantiles.

```{r}
pgeom(20, prob = 0.05, log.p = FALSE)  # probability of a succes within fist 20 trials
1- pgeom(20, prob = 0.05, log.p = FALSE)  # 
```
The probability that we interview 20 patients and don't find the dessease is 0.34




