---
title: "Homework 2. Functions"
author: "Nina Dyatchenko"
date: "January 27th, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Quiz

1) What are the three components of a function?

Body
Arguments
Environment

2) What does the following code return?
```{r}
x <- 10
f1 <- function(x) {
  function() {
    x + 10
  }
}
f1(1)()
```
The function returns a number 11. The function sums a given numeric argument with a number 10.

3) How would you more typically write this code?
```{r}
`+`(1, `*`(2, 3))

1+ 2*3
```

4) How could you make this call easier to read?
```{r}
mean(, TRUE, x = c(1:10, NA))

mean(x = c(1:10, NA), na.rm = TRUE)
```

5) Does the following function throw an error when called? Why/why not?
```{r}
f2 <- function(a, b) {
  a * 10
}
f2(10, stop("This is an error!"))
```
No, the error does not occure becouse the argument b is not used in the environment of the function.

6) What is an infix function? How do you write it? 
Infix function thet is input between the two arguments. Infix functions are + , - , *, /, ^ and others.To write an infix function, the new operator has to be inclosed with %.

What’s a replacement function? How do you write it?
```{r}
`second<-` <- function(x, value) {
  x[2] <- value
  x
}
x <- 1:10
second(x) <- 5L
x

```
Replacement function acts like it modify its arguments in place. The name of the function is inclosed by  backticks and ends with "get" operator <- as such: `name<-`. 

7) What function do you use to ensure that a cleanup action occurs regardless of how a function terminates?